---
title: "assess predictions"
format: html
---

## ideas

list all prediction files, get their mtimes or pull date out of filename
or even combine, replacing an earlier prediction by a later one

get all results, filter the ones between desired dates
place side by side with predictions
compute log lik
simulate log lik
see where on distribution


## packages

```{r}
library(tidyverse)
source("functions.R")
source("assess-pred.R")
```

## get preds

```{r}
pred_files <- get_prediction_times()
all_predictions <- get_all_predictions(pred_files)
# all_predictions
all_results <- get_all_results(leagues)
# all_results
```


## combine and simulate

```{r}
res_prob <- combine_resprob(all_predictions, all_results)
res_prob
# res_prob %>% slice_sample(n = 1000) -> res_prob
# summary(res_prob)
obs_ll <- calc_loglik(res_prob)
obs_ll
sim_loglik(1000, res_prob) %>% 
  ggplot(aes(x = loglik)) + geom_density() + geom_vline(xintercept = obs_ll)
```

observed ll is off the bottom of the distribution from the sims, so the things that happened are too unlikely
maybe that suggests using a neg bin rather than a poisson, or using a stronger equality prior


