---
title: "rate"
format: html
---

## Packages

```{r}
library(tidyverse)
library(posterior)
library(cmdstanr)
options(mc.cores = 4)
source("functions.R")
source("rate_functions.R")
source("predictions_functions.R")
```

## next rate thing

I have added first place and team ranks to the display.
Catch up on it during next week or two (as in, does it seem to be working?)

```{r}
all_next_rate_date(leagues) -> leagues0
leagues0 %>% select(fname, next_rate, dow) 
leagues0  %>% 
  filter(next_rate < now()) -> leagues1
```

jot: ones I want to do

```{r}
# leagues0 %>%
#   filter(str_detect(fname, "isl")) -> leagues1
# leagues1
```

## pass the relevant ones from there into here (slice leagues to do just a few / specific ones; DO NOT do them all! Though this might be all right now I fixed the next rate date.)

```{r}
leagues1 %>% update_rate() 
```

## rating rank

```{r}
make_rank_table <- function(fname) {
  rat <- read_rds(str_c("fit/", fname))
  rat %>% as_draws_df() %>% 
    summarise_draws("mean") %>% 
    filter(str_detect(variable, "^[od]")) %>% 
    separate_wider_position(variable, widths = c(od = 1, num_txt = 4), too_few = "align_start") %>% 
    mutate(id = parse_number(num_txt)) %>% 
    group_by(id) %>% 
    summarize(rat = sum(mean)) %>% 
    mutate(rk = rank(-rat)) %>% 
    select(id, rk) -> rank_table
  lu <- read_rds(str_c("lu/", fname))
  lu %>% left_join(rank_table, join_by("id")) %>% 
    select(team, rk) -> team_ranks
  team_ranks
}
leagues %>% 
  # slice_sample(n = 5) %>% 
  rowwise() %>% 
  mutate(fname = make_fname(country, league, season, part, prefix = "")) %>% 
  select(fname) %>% 
  mutate(rank_table = list(make_rank_table(fname))) %>% 
  unnest(rank_table) -> all_ranks
all_ranks
```

\]

## predictions for upcoming games based on most recent ratings

```{r}
#| warning: false

my_fname <- "predictions.rds"
my_xname <- str_c("preds", now(), ".rds")
file.copy(my_fname, my_xname)
leagues %>% mutate(r = row_number()) %>% 
  rowwise() %>% 
  mutate(fname = make_fname(country, league, season, part, prefix = "")) %>% 
  mutate(mtime = file.mtime(str_c("fit/", fname))) %>% 
  mutate(size = file.size(str_c("fit/", fname))) %>% 
  filter(!is.na(mtime)) %>% 
  filter(size > 100) %>% 
  ungroup() %>% 
  slice_sample(n = 999) %>%
  pull(fname) %>% 
  map(\(x) league_preds(x)) %>% bind_rows() %>% arrange(ko) -> predictions
predictions %>% 
  left_join(all_ranks, join_by(fname, t1 == team)) %>% 
  left_join(all_ranks, join_by(fname, t2 == team)) %>% 
  select(fname, ko, t1, r1 = rk.x, r2 = rk.y, t2, `2`, `1`, `0`) -> predictions2
write_rds(predictions2, "predictions.rds")
```

display some of these predictions

```{r}
now <- now()
read_rds("predictions.rds") %>% 
  filter(between(ko, now - hours(3), now + hours(2))) %>% 
  arrange(fname) %>% 
  View()
```
